Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-22 journal/article.tex
S: Communicating the change

@@

>>>>

* Some success factors are compiled from ``what we learned'' or ``advice for
  others'' lists. We considered whether the advice was something the
  organization had tried in practice.

@@

\subsubsection{Communication and transparency in the change}

Intensive communication was emphasized in a number of studies. It is important
to reach a maximum number of people throughout the organization, as without
communiction the a new model will not take root [P16, P43].
It was recommended that use of the new model is made highly visible on many
communication channels and even over-communicated [P16, P33, P41]. Mencke [P33]
summarizes the viewpoint on over-communication: ``Even if you think that your
teams understand a new method or process, repeat your communication to be
sure.'' Workshops, coaching sessions, online discussions, and newletters are
examples on different communication formats used [P41]. Another approach in
communicating the change was that managers explained and encouraged change in an
extensive series of one-to-one discussions [P22].

Enabling transparency during the transformation was another communication
related theme that was brought up, and even highlighted as a critical factor for
success [P11, P16]. Fry and Greene [P16] underline the importance of
transparency and sharing of information: ``This bias to sharing information with
everyone was critical in our ability to adapt on a daily basis to ensure our
success.'' Transparency was achieved by showing both successes and challenges
[P6], actively reaching out for feedback [P6], using project management tools to
display project status publicly [P11], by rearranging physical spaces [P42], and
by holding the meetings of the rollout team in public [P16].
By sharing experiences and status of the transformation the organization was
aligned and everyone was moving in the same direction [P42, P43].

% The inertia and fear of sharing information must be overcome [P33].

% Sharing everything with everyone was key to success [P16].

% Organizations made also an effort to communicate the status of the
% transformation [P16, P43].

% Because of the volatility of software development there must be continuous and
% fluent communication between managers, POs, and teams [P42].

Communicating the goals of the transformation was highlighted in a some studies.
Having a clear message of expectations helped to remove confusion and make
people understand the purpose of the transformation [P43, P48]. The motivation
to change can be increased by having a simple proposal on how to reach the
desired outcomes [P40].
